Model Finding for Recursive Functions in SMT

### 2015-04-29 tex/main.tex
more

Alloy (and Alloy idiom by Kuncak \& Jackson)
The model finder for KIV based on Alloy
Nitpick
Leon

>>>>

first-order model finders: SEM, MACE/Mace, Paradox, iProver
  either direct search or reduction to SAT

Alloy (and Alloy idiom by Kuncak \& Jackson), Kodkod
The model finder for KIV based on Alloy
Nitpick
Leon
